### 2019-07-04 README.Rmd
adds coverage reporting

<!-- Code status -->
[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=master)](https://travis-ci.org/ProvTools/Rclean) 
[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean)

@@

```{r}
options(prov.json = readLines("prov_micro.json"))
```

@@

```{r}
clean(rp = TRUE)

@@

```{r}
clean(x, rp = TRUE)

>>>>

<!-- Code status -->
[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=master)](https://travis-ci.org/ProvTools/Rclean) 
[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean) 
[![Coverage status](https://codecov.io/gh/provtools/Rclean/branch/tests/graph/badge.svg)](https://codecov.io/github/provtools/Rclean?branch=tests)

@@

```{r eval = FALSE}
options(prov.json = readLines("prov_micro.json"))
```

@@

```{r eval = FALSE}
clean(rp = TRUE)

@@

```{r eval = FALSE}
clean(x, rp = TRUE)
